Summary of models

### 2022-07-13 Models.Rmd
correlation and summary of models

---
title: "Summary of models"
output: pdf_document
date: '2022-07-08'
---

@@

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)

@@

corre %>% 
   kable(booktabs = TRUE,digits =  4,longtable = T,linesep = c("","","","","","\\addlinespace"),align = "llcccccc") %>%
  kable_styling(font_size = 9,full_width = F)

@@

@@

Summary of models for fruit proportion per plant species

**Richness**

@@

@@

ta_f %>% 
    kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )

@@

\newpage
**Visitation rate**

@@

ta_f2 %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )

@@

Summary of models for seed numbers per plant species

**Richness**
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

@@

ta_seed %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )

@@

\newpage
**Visitation rate**

@@

ta_seed2 %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )
```

@@

Summary of models for seed weight per plant species

**Richness**

@@

ta_weight %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )

@@

**Visitation rate**

@@

ta_weight2 %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )

@@

>>>>

---
title: "Summary of models"
output: pdf_document
date: '2022-07-08'

---

@@

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)

@@

corre %>% 
   kable(booktabs = TRUE,digits =  4,longtable = T,linesep = c("","","","","","\\addlinespace"),align = "llcccccc") %>%
  kable_styling(font_size = 9,full_width = F, position="left")

@@

```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side, out.width="100%",fig.fullwidth=TRUE}

library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggcorrplot)

df_with_plots <- a %>%
  group_by(Plant_gen_sp) %>%
  nest() %>%
  mutate(plot = map(data, function(.x) {
    .x  %>%
      cor() %>%
      ggcorrplot::ggcorrplot()
  }))

plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))

plots1[[1]] + plots1[[2]] + plots1[[2]] + plots1[[2]]

\clearpage

@@

Summary of models for fruit proportion per plant species. Binomial cbind(fruit_formado, Fruit_No). Site_ID as factor random

## Richness

@@

Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

@@

ta_f %>% 
    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Visitation rate

@@

ta_f2 %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

## Frequency

Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

# frequency
ta_f3<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_f3<-ta_f3 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_f3<-filter(ta_f3, !term == "sd__(Intercept)")

ta_f3 %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(ta_f3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

Summary of models for seed numbers per plant species (LMM). Site_ID as factor random

## Richness

@@

ta_seed %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

\newpage
## Visitation rate

@@

ta_seed2 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
```

\newpage
## Visitation rate

# Frequency
ta_seed3<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_seed3<-ta_seed3 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed3<-filter(ta_seed3, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed3 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

Summary of models for seed weight per plant species (LMM). Site_ID as factor random

## Richness

@@

ta_weight %>% 
kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Visitation rate

@@

ta_weight2 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

@@

## Frequency

#Models _ Seed weight 
# frequency
ta_weight3<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

ta_weight3<-ta_weight3 %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_weight3<-filter(ta_weight3, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_weight3 %>% 
kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_weight3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")
